### 2025-07-22 paper/sections/other/main_results.qmd
nearly there

# Divergence-based:
y = "mmd"
df_mmd = aggregate_ce_evaluation(
    res_dir;
    y
    return_sig_level=false, 
    conf_int=lvls,
    agg_further_vars=["run", "lambda_energy_eval"],
)
df_mmd.measure .= y
df = innerjoin(df_mtbl, df_ip, df_mmd; on=:dataset)
```

>>>>

# Divergence-based:
y = "mmd"
df_mmd = aggregate_ce_evaluation(
    res_dir;
    y,
    return_sig_level=false, 
    conf_int=lvls,
    agg_further_vars=["run", "lambda_energy_eval"],
)
df_mmd.measure .= y
df = vcat(df_mtbl, df_ip, df_mmd)
Serialization.serialize("paper/experiments/output/ci.jls", df)
```

```{julia}
#| output: asis
#| label: tbl-ci
#| tbl-cap: "Confidence Intervals"

df = Serialization.deserialize("paper/experiments/output/ci.jls")
df = select(df, :variable, :dataset, :full, :vanilla, "99.0%")
df = transform(df, "99.0%" => AsTable) |>
    df -> select(df, Not("99.0%"))
rename!(df, :dataset => :data, :x1 => :LB, :x2 => :UB)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...]
)

```
